%%% Copyright (C) 2004 Claire M. Connelly and 
%%% the Department of Mathematics, Harvey Mudd College.
%%%
%%% This file is part of the sample thesis document provided to HMC
%%% mathematics students.
%%%
%%% See the COPYING document, which should accompany this
%%% distribution, for information about distribution and modification
%%% of the document and its components.

\chapter{Conclusion}%
\label{sec:typesetting}

We conclude the year with the following accomplishments. We successfully built:

\begin{itemize}
    \item A launched website, created with the support of PilotCity's local team, which is already being used by PilotCity's academic and industry partners. 
    \item A maintainable, scalable Google Cloud database with secure log-in and optimized data structures.
    \item A recommendation engine to match classrooms and employers for projects. This engine: 
    \begin{itemize}
        \item harnesses Natural Language Processing tools like the GloVe model to place similarity scores on user inputs such as course names, industry preferences and project descriptions.
        \item outputs a ranked list of candidate classrooms/employers who are closely related. This list enables employers and teachers to easily discover each other for future partnerships.
    \end{itemize} 

    \item A module for visualization of educational priorities using topic modeling techniques. Features of this module include:
    \begin{itemize}
        \item Training a topic model on any collection of PDF documents. 
        \item Flexibility in the type of topic modelling techniques used. Currently, the module supports LDA and NMF. 
        \item Automated selection of optimal number of topics based on topic coherence.
        \item Visualizations of the topic distributions of an input PDF document. 
         
    \end{itemize}
    \item An engine that generates a guide for students which enumerates and defines the most important keywords contained in a classroom syllabus.  
\end{itemize}

Each stage of this project has been an iterative process involving multiple rounds of interviews and conversations with tech companies, school district administrators, high school teachers and other stakeholders to fully understand the impact of our work. From these interactions, our team has gained many insights about the educational system and the application of Natural Language Processing and automation to improve educational experiences.

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "master"
%%% End: 
