\chapter{Versions of the Sample Thesis/Clinic Report}
\label{ch:previous_versions}

This document is based, in part, on earlier versions of sample
Clinic reports and sample theses.  Some material from those versions
is included nearly intact in this document, whereas other material
has been written from scratch or adapted from other sources.

The authors of the present work would like to acknowledge and thank
Professor Lesley Ward for her original sample thesis report, created
in 1999.  She and Jeremy Rouse (HMC~2003) revised that document in
the year 2000.

The current version of the document is based on the updated sample
thesis created in 2003 by Claire~M. Connelly, the Department of
Mathematics Systems Administrator.  The original sample Clinic
report was based on this sample thesis document.

In 2005, Claire merged the sample thesis and sample Clinic reports,
making maintenance and distribution a bit easier.


\section{Comments, Problems, and Updates}
\label{sec:feedback}

The department is eager to receive feedback from users of the sample
document so that we can improve it.  We are especially interested in
any problems that you may have in compiling the document, but
advice, questions, and updates to the content are also welcome.

Please send such comments and ``bug reports'' to us at
\textsf{latex@math.hmc.edu}.  If possible, please tell us where you
downloaded the document's source code, and what version and date are
noted in the master file for the document you're working with.


